---
output: pdf_document
---

------------------------------------------------------------------------

------------------------------------------------------------------------

## WA K-function

```{r}
if (!require("spatstat.Knet")) {
  # Install the latest version of the package
  install.packages("spatstat.Knet_1.11-0.tar.gz", repos = NULL, type = "source")
  if (!require("spatstat.Knet")) 
    stop("Unable to install package")
} else requireversion(spatstat.Knet, "1.11-0")

library(spatstat.geom)
library(spatstat.linnet)
library(spatstat)
library(sf)        # 
library(dplyr)     # 

# Data Loading -----------------------------------------------------------------
data("wacrashes", package = "spatstat.Knet")
X_sub1 <- readRDS("Rakshit/WAsub_data/X_sub.rds")
X_sub2 <- readRDS("Rakshit/WAsub_data2/X_sub.rds")
```

### 1. Projection

Firstly, I considered the unit and the projection of the selected area.

```{r}
W <- as.owin(domain(wacrashes))
W1 <- as.owin(domain(X_sub1))
W2 <- as.owin(domain(X_sub2))
W$xrange ; W$yrange
W1$xrange ; W1$yrange
W2$xrange ; W2$yrange
```

And i think there is no problem about the projection.

### 2. Calculating function

I compared the K-function calculated by Knet with by linearK.

```{r}
# r_grid <- seq(0, 1000, length = 20) # meter
# Khom1 <- Knet(X_sub1,r = r_grid)
# 
# plot(Khom1, legend = FALSE, lwd = 2, main = "")
```

```{r}
r_grid <- seq(0, 10000, length = 100) # meter
Khom2 <- Knet(X_sub2,r = r_grid)

plot(Khom2, legend = FALSE, lwd = 2, main = "")

plot(linearK(X_sub2,correction="none"))
plot(linearK(X_sub2), add = TRUE)
plot(linearK(X_sub2))
```

It means the issue is not caused by Knet or the issue exists in both two function.

```{r}
r_grid <- seq(0, 10000, length = 100) # meter
Khom2 <- Knet(X_sub2,r = r_grid)

plot(Khom2, legend = FALSE, lwd = 2, main = "")
```

### 3.GADM

```{r}
AUS2 <- st_read("gadm41_AUS/gadm41_AUS_2.shp")
# loading the GADM 

WA <- subset(AUS2, NAME_1 %in% c("Western Australia","Western Australia (state)"))

#Projection : 28350
WA_mga50 <- st_transform(WA, 28350)   # unit:meter
AUS2_mga50 <- st_transform(AUS2, 28350)   # unit:meter

plot(st_geometry(AUS2_mga50), col = "grey95", border = "grey70")
plot(X_sub2, add = TRUE, col = "black", lwd = 0.8)
plot(X_sub1, add = TRUE, col = "red", lwd = 0.8)

plot(st_geometry(WA_mga50), col = "grey95", border = "grey70")
plot(X_sub2, add = TRUE, col = "black", lwd = 0.8)
plot(X_sub1, add = TRUE, col = "red", lwd = 0.8)
```

It looks very close to Perth’s real location . But the data 'wacrashes' don't mention the projection it used, so i don't know if there is a projection more accurate.

But it might mean the K-function issue not be caused by map size.

Then I consider to separate the X_sub2 into smaller area and test the K-function.

### 4.Smaller area test

```{r}
W2$xrange ; W2$yrange

xr <- W2$xrange; yr <- W2$yrange
xmid <- xr[1] + 0.45*(xr[2] - xr[1])
W_left  <- owin(xrange = c(xr[1], xmid), yrange = yr)
W_right <- owin(xrange = c(xmid,   xr[2]), yrange = yr)

X_left  <- X_sub2[W_left,  clip = TRUE, drop = TRUE]
X_right <- X_sub2[W_right, clip = TRUE, drop = TRUE]

plot(X_left); plot(X_right)
```

```{r}
r_grid <- seq(0, 50000, length = 100) # meter
Khom_L <- Knet(X_left,r = r_grid)
Khom_R <- Knet(X_right,r = r_grid)

plot(Khom_L, legend = FALSE, lwd = 2, main = "")
#plot(Khom_R, legend = FALSE, lwd = 2, main = "")
```

### 5. Adding points test

```{r}
L  <- domain(X_sub2) 
X_sim  <- runiflpp(400, L)             # npoints(X_sub2) = 72 
X_sub2plus  <- superimpose(X_sub2, X_sim)

r_grid <- seq(0, 1000, length = 100) # meter
Khom_sim <- Knet(X_sub2plus,r = r_grid)

plot(Khom_sim, legend = FALSE, lwd = 2, main = "")
```

So I still think the reason why the X_sub2's K-function goes high sharply is the clustering in the lower central part of X_sub2. I think next step is to understand the correction the Knet function did.

## Manchester GADM

```{r}
## Manchester data
X_manCity <- readRDS("Manchester/CM_data/X_manCity.rds")

GBR4 <- st_read("gadm41_GBR/gadm41_GBR_4.shp")
# loading the GADM 


GBR4_trans <- st_transform(GBR4, 27700)   # unit:meter

plot(st_geometry(GBR4_trans), col = "grey95", border = "grey70")
plot(X_manCity, add = TRUE, col = "red", lwd = 0.8)

# r <- seq(0, 1000, length = 20)
# 
# K_hom_manCity <- Knet(X_manCity, r = r)
# plot(K_hom_manCity, main = "Homogeneous K on Linear Network", legend = FALSE, lwd = 2)
```

```{r}
library(spatstat.geom)
library(spatstat.linnet)
library(spatstat)
library(sf)        # 
library(dplyr)     # 
```
